Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2018-10-24 awipev-CO2.Rmd
ajout des paths pour les photos + dossier Images

<div style="text-align:center" markdown="1">
  <img  src="./Images/Outside/Container.png" width="200" height="200">
  <img  src="./Images/Outside/Intake.png" width="200" height="200">
  <img  src="./Images/FerryBox/2018-04-17_Ferrybox2.jpg" width="200" height="200">
</div>

@@

<div style="text-align:center" markdown="1">
<img  src="./Images/Salt/2016-04-04_leakage_AT_analyser1.jpg" width="200" height="200">
<img  src="./Images/Salt/2016-04-04_leakage_AT_analyser3.jpg" width="200" height="200">
</div>

>>>>

<div style="text-align:center" markdown="1">
  <img  src="./Images/Container.png" width="200" height="200">
  <img  src="./Images/Intake.png" width="200" height="200">
  <img  src="./Images/2018-04-17_Ferrybox2.jpg" width="200" height="200">
</div>

@@

<div style="text-align:center" markdown="1">
<img  src="./Images/2016-04-04_leakage_AT_analyser1.jpg" width="200" height="200">
<img  src="./Images/2016-04-04_leakage_AT_analyser3.jpg" width="200" height="200">
</div>
